---
title: "Growth of Orange Trees"
author: "Francesca Tantardini"
date: "20 May 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



## The dataset Orange
The **Orange** data frame collects data about the growth of 5 orange trees. It consists of 36 observation of 3 variables: 

- the tree the measurements refer to
- the **age** (days since December 31, 1968) 
- the **circumference** (mm).


In the following we 

- show a scatterpot of the data
- fit a linear model with age as predictor for circumference 


## Circumference vs Age for Trees Nr. 1 to 5

```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.height=5.5}
library(plotly)
plot_ly(Orange, x=~age, y=~circumference, color=~Tree, type="scatter")
```

## Fitting a linear Model

We fit a linear model for the outcome circumference with age as regressor 

```{r, message=FALSE, warning=FALSE, echo=TRUE}
fitAll<-lm(circumference~age, Orange)
summary(fitAll)$coefficients
```

## Fitting a linear Model
```{r, message=FALSE, warning=FALSE}
df<-data.frame(Orange, fit=fitAll$fitted.values, res=fitAll$residuals)
```
```{r, message=FALSE, warning=FALSE, fig.height=5.5}
plot_ly(df, x=~age)%>%
    add_trace(y=~fit, mode='lines', name='linear model')%>% 
    add_trace(y=~circumference, color=~Tree, mode='markers')%>% 
layout(yaxis = list (title = 'Circumference (mm)'))
```

## Plot of the Residuals

```{r, warning=FALSE, message=FALSE, fig.height=5.5}
plot_ly(data.frame(age=Orange$age, res=fitAll$residuals, tree=Orange$Tree), x=~age, y=~res, type = "scatter" , color=~tree) %>%
layout(yaxis = list (title = 'Residuals (mm)'))
```

